D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-06 ootavacuous.tex
"Non-Trivial Semantic Dependencies": Fix HW/compiler comparison
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

One might ask why semantic dependencies can be nontrivial when hardware
address, control, and data dependencies are much more straightforward.
The reason is that, unlike compilers, hardware:
(1)~Respects dependencies even when they reduce to a constant,
(2)~Less-aggressively optimizes, and
(3)~Lacks undefined behavior.

>>>>

One might ask why semantic dependencies can be complicated when hardware
address, control, and data dependencies are much more straightforward.
The reason is that, unlike compilers, hardware:
(1)~Respects dependencies even when they reduce to a constant,
(2)~Optimizes much less aggressively, if at all, and
(3)~Lacks undefined behavior.
